A Comparison of Graph Processing Systems

### 2020-09-15 documentation/paper/main.tex
kleine fixes von der Rückmeldung und Polymer Overview
new references

\begin{abstract}
TODO
\end{abstract}

@@

\section{Introduction}
% In recent years graph sizes have increased significantly [?] .
% Thus performance and memory efficiency of the graph analysis applications is now more important than ever.

@@

\section{Discussion}

\section{Conclusion}

@@

\section*{Acknowledgments}
We are using the graph frameworks Galois~\cite{Galois}, Ligra~\cite{Ligra}, Polymer~\cite{Polymer}, Gemini~\cite{Gemini} as well as Apache Giraph~\cite{Giraph}.

Also we use Gluon~\cite{vertGalois} for the distributed Galois setups.

Gemini~\cite{Gemini}

%We would like to thank our supervisor Heiko Geppert for continued guidance and support.

\appendices
\section{Installation Guides}\label{app:installationGuides}
The complete installation guides with steps on how to run the same algorithms we used is available in our repository\footnote{\url{https://github.com/SerenGTI/Forschungsprojekt/tree/master/documentation}}

@@

% \bibliographystyle{IEEEtran}
% \bibliography{literature}

@@

@@

\bibitem{pagerank}
\BIBentryALTinterwordspacing
S.~Brin and L.~Page, ``Reprint of: The anatomy of a large-scale hypertextual
  web search engine,'' \emph{Computer Networks}, vol.~56, no.~18, pp. 3825 --
  3833, 2012, the WEB we live in. [Online]. Available:
  \url{http://www.sciencedirect.com/science/article/pii/S1389128612003611}
\BIBentrySTDinterwordspacing

@@

@@

\bibitem{snap}
\BIBentryALTinterwordspacing
Stanford~University. (2020, Sep.) Stanford network analysis project. [Online].
  Available: \url{https://snap.stanford.edu}
\BIBentrySTDinterwordspacing

@@

% Alles bis hier kommt aus main.bbl

>>>>

\begin{abstract}
\todo{Section}
\end{abstract}

@@

\section{Introduction}
\todo{Section}
% In recent years graph sizes have increased significantly [?] .
% Thus performance and memory efficiency of the graph analysis applications is now more important than ever.

@@

\section{Discussion}
\todo{Section}

\section{Conclusion}
\todo{Section}

@@

\section*{Acknowledgments}
%We would like to thank our supervisor Heiko Geppert for his continued guidance and support.

\appendices
\todo{Beide zusammenfassen}
\section{Installation Guides}\label{app:installationGuides}
The complete installation guides with steps on how to run the same algorithms we used is available in our repository\footnote{\url{https://github.com/SerenGTI/Forschungsprojekt/tree/master/documentation}}

@@

%\bibliographystyle{IEEEtran}
%\bibliography{literature}

@@

\bibitem{newman2010networks}
\BIBentryALTinterwordspacing
M.~Newman, \emph{Networks: An Introduction}.\hskip 1em plus 0.5em minus
  0.4em\relax OUP Oxford, 2010. [Online]. Available:
  \url{https://books.google.de/books?id=-DgTDAAAQBAJ}
\BIBentrySTDinterwordspacing

@@

\bibitem{pagerank}
\BIBentryALTinterwordspacing
S.~Brin and L.~Page, ``The anatomy of a large-scale hypertextual web search
  engine,'' \emph{Computer Networks and ISDN Systems}, vol.~30, no.~1, pp. 107
  -- 117, 1998, proceedings of the Seventh International World Wide Web
  Conference. [Online]. Available:
  \url{http://www.sciencedirect.com/science/article/pii/S016975529800110X}
\BIBentrySTDinterwordspacing

\bibitem{tao}
\BIBentryALTinterwordspacing
K.~Pingali, D.~Nguyen, M.~Kulkarni, M.~Burtscher, M.~A. Hassaan, R.~Kaleem,
  T.-H. Lee, A.~Lenharth, R.~Manevich, M.~M\'{e}ndez-Lojo, D.~Prountzos, and
  X.~Sui, ``The tao of parallelism in algorithms,'' in \emph{Proceedings of the
  32nd ACM SIGPLAN Conference on Programming Language Design and
  Implementation}, ser. PLDI '11.\hskip 1em plus 0.5em minus 0.4em\relax New
  York, NY, USA: Association for Computing Machinery, 2011, p. 12–25.
  [Online]. Available: \url{https://doi.org/10.1145/1993498.1993501}
\BIBentrySTDinterwordspacing

@@

\bibitem{hugepages}
\BIBentryALTinterwordspacing
A.~Panwar, A.~Prasad, and K.~Gopinath, ``Making huge pages actually useful,''
  in \emph{Proceedings of the Twenty-Third International Conference on
  Architectural Support for Programming Languages and Operating Systems}, ser.
  ASPLOS '18.\hskip 1em plus 0.5em minus 0.4em\relax New York, NY, USA:
  Association for Computing Machinery, 2018, p. 679–692. [Online]. Available:
  \url{https://doi.org/10.1145/3173162.3173203}
\BIBentrySTDinterwordspacing

\bibitem{origGalois}
\BIBentryALTinterwordspacing
M.~Kulkarni, K.~Pingali, B.~Walter, G.~Ramanarayanan, K.~Bala, and L.~P. Chew,
  ``Optimistic parallelism requires abstractions,'' in \emph{Proceedings of the
  28th ACM SIGPLAN Conference on Programming Language Design and
  Implementation}, ser. PLDI '07.\hskip 1em plus 0.5em minus 0.4em\relax New
  York, NY, USA: Association for Computing Machinery, 2007, p. 211–222.
  [Online]. Available: \url{https://doi.org/10.1145/1250734.1250759}
\BIBentrySTDinterwordspacing

@@

\bibitem{snap}
\BIBentryALTinterwordspacing
{Stanford University}. (2020, Sep.) Stanford network analysis project.
  [Online]. Available: \url{https://snap.stanford.edu}
\BIBentrySTDinterwordspacing

@@
